Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2014-08-01 paper.tex
last fixes for acm submission

\newcommand{\comment}[1]{\textcolor{red}{\bf #1}}
%\newcommand\comment[1]{} % When you enable this lines, all the notes will disappear

@@

@@

\title{Parameter Space Representation of Pareto Front to
Explore Hardware-Software Dependencies}
\author{VINCENZO CATANIA
\affil{University of Catania}
ANDREA ARALDO
\affil{University of Catania}
DAVIDE PATTI
\affil{University of Catania}
}

%\maketitle
\begin{abstract}
Embedded Systems Design requires conflicting objectives to be
optimized with an appropriate choice of hardware/software parameters.
A simulation campaign can guide the design in finding the best
trade-offs, but due to the big number of possible configurations it
is often unfeasible to simulate all of them. For these reasons Design Space
Exploration (DSE) algorithms aim at finding near-optimal system
configurations only simulating a subset of them.

In this work we present PS, a new multiobjective exploration
algorithm. The basic idea is to recognize \emph{interesting} regions, i.e.
regions of the configuration space that are proving to provide better
configurations with regard to other ones. PS evaluates more configurations in
interesting regions while exploring less thoroughly the rest of the
configuration space. After a detailed formal description of the
algorithm and the underlying concepts, we show a 
case study involving the hardware/software exploration of a VLIW
architecture. Qualitative and quantitative comparisons of PS
against a well-know multiobjective genetic approach demonstrate that,
while not outperforming it in terms of dominance, the proposed
approach can trade the uniformity and granularity qualities of the
solutions found for obtaining larger Pareto sets, thus representing a
further choice for designer when objective constrains allow it.
\end{abstract}

@@

\begin{bottomstuff}
Author's addresses: V. Catania, DIEEI University of Catania;
A. Araldo, DIEEI University of Catania;
D. Patti, DIEEI University of Catania.
\end{bottomstuff}

>>>>

%\newcommand{\comment}[1]{\textcolor{red}{\bf #1}}
\newcommand\comment[1]{} % When you enable this lines, all the notes will disappear

@@

% Metadata Information
%\acmVolume{9}
%\acmNumber{4}
%\acmArticle{39}
%\acmYear{2010}
%\acmMonth{3}

@@

\title{Parameter Space Representation of Pareto Front to
Explore Hardware-Software Dependencies}
\author{VINCENZO CATANIA
\affil{University of Catania}
ANDREA ARALDO
\affil{Universit\'e Paris-Sud and Telecom ParisTech, Telecom ParisTech
Paris, France;}
DAVIDE PATTI
\affil{University of Catania}
}

%\maketitle
\begin{abstract}
%Embedded Systems Design requires conflicting objectives to be
%optimized with an appropriate choice of hardware/software parameters.
%In this work we present PS, a new multiobjective exploration algorithm
%exploiting the parameter space representation of the pareto front.
%After a detailed formal description of the algorithm and the
%underlying concepts, we show a case study involving the
%hardware/software exploration of a VLIW architecture. Qualitative and
%quantitative comparisons of the PS approach against a well-known
%multiobjective genetic technique demonstrate that, while not
%outperforming it in terms of pareto dominance, the proposed approach
%can trade the uniformity and granularity qualities of the solutions
%found for obtaining larger Pareto sets, thus representing a further
%choice for designer when objective constrains allow it.

Embedded Systems Design requires conflicting objectives to be
optimized with an appropriate choice of hardware/software parameters.
A simulation campaign can guide the design in finding the best
trade-offs, but due to the big number of possible configurations it
is often unfeasible to simulate all of them. For these reasons Design Space
Exploration (DSE) algorithms aim at finding near-optimal system
configurations only simulating a subset of them.

In this work we present PS, a new multiobjective exploration
algorithm. The basic idea is to recognize \emph{interesting} regions, i.e.
regions of the configuration space that are proving to provide better
configurations with regard to other ones. PS evaluates more configurations in
interesting regions while exploring less thoroughly the rest of the
configuration space. After a detailed formal description of the
algorithm and the underlying concepts, we show a 
case study involving the hardware/software exploration of a VLIW
architecture. Qualitative and quantitative comparisons of PS
against a well-known multiobjective genetic approach demonstrate that,
while not outperforming it in terms of pareto dominance, the proposed
approach can trade the uniformity and granularity qualities of the
solutions found for obtaining larger Pareto sets, thus representing a
further choice for designer when objective constrains allow it.
\end{abstract}

@@

\begin{bottomstuff}
Author's addresses: V. Catania, DIEEI University of Catania;
A. Araldo, Universit\'e Paris-Sud and Telecom ParisTech, Telecom ParisTech
Paris, France;
D. Patti, DIEEI University of Catania.
\end{bottomstuff}
